MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-22 papers/webservice-coalition-learning/webservice_coalition_learning.tex

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&{\bigg(\big((\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)}
\end{split}
\end{equation}

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&{\bigg(\big((\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)}
\end{split}
\end{equation}

@@

\section{Experimental Results and Analysis}\label{s:resutls}

text text \cite{ICWS2011-1}

>>>>

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
\end{split}
\end{equation}

@@

\subsection{Learning Date}\label{ss:learningdata}

\subsubsection{web services}\label{sss:webservices}
\subsubsection{filtered data}\label{sss:filtereddata}
\subsubsection{feature engineering}\label{sss:feng}
\subsubsection{feature vector generation}\label{sss:fvg}

\subsection{Learning Model}\label{ss:learningmodel}

\subsubsection{training data set}\label{sss:tds}
\subsubsection{cross validation data set}\label{sss:cvds}
\subsubsection{sigmoid learned hypothesis function}\label{sss:slh}
\subsubsection{rationalized decision maker}\label{sss:rdm}
